### 2016-09-18 paper.tex
Remove citations from abstract; resolves #75
Regenerate bibliography in order; resolves #74

The mechanical power, total rotor drag, and near-wake velocity of a 1:6 scale
model (1.075 m diameter) of the US Department of Energy's Reference Model
vertical-axis cross-flow turbine were measured experimentally in a towing tank,
to provide a comprehensive open dataset for validating numerical models.
Performance was measured for a range of tip speed ratios and at multiple
Reynolds numbers by varying the rotor's angular velocity and tow carriage speed,
respectively. A peak power coefficient $C_P = 0.37$ and rotor drag coefficient
$C_D = 0.84$ were observed at a tip speed ratio $\lambda_0 = 3.1$. A regime of
weak linear $Re$-dependence of the power coefficient was observed above a
turbine diameter Reynolds number $Re_D \approx 10^6$. The effects of support
strut drag on turbine performance were investigated by covering the rotor's NACA
0021 struts with cylinders. As expected, this modification drastically reduced
the rotor power coefficient. Strut drag losses were also measured for the NACA
0021 and cylindrical configurations with the rotor blades removed. For
$\lambda=\lambda_0$, wake velocity was measured at 1 m $(x/D=0.93)$ downstream.
Mean velocity, turbulence kinetic energy, and mean kinetic energy transport were
compared with results from a high solidity turbine acquired with the same test
apparatus. Like the high solidity case, mean vertical advection was calculated
to be the largest contributor to near-wake recovery. However, overall, lower
levels of streamwise wake recovery were calculated for the RM2 case---a
consequence of both the relatively low solidity and tapered blades reducing
blade tip vortex shedding---responsible for mean vertical advection---and lower
levels of turbulence caused by higher operating tip speed ratio and therefore
reduced dynamic stall. Datasets, code for processing and visualization, and a
CAD model of the turbine have been made publicly available
\cite{Bachant2016-RM2-data,Bachant2015-RM2-CAD}.

@@

% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
%
\bibliographystyle{plos2015}
%\bibliography{library}
\begin{thebibliography}{10}

@@

    \bibitem{Neary2014a}
    Neary VS, Lawson M, Previsic M, Copping A, Hallett KC, A L, et~al.
    \newblock Methodology for design and economic analysis of marine energy
    conversion (MEC) technologies.
    \newblock In: Proceedings of the Marine Energy Technology Symposium (METS2014).
    Seattle, WA; 2014. .

@@

    \bibitem{Murray2011}
    Murray J, Barone M.
    \newblock The Development of CACTUS, a Wind and Marine Turbine Performance
    Simulation Code.
    \newblock In: Proceedings of the 49th AIAA Aerospace Sciences Meeting including
    the New Horizons Forum and Aerospace Exposition; 2011. .

@@

    \bibitem{Bachant2014}
    Bachant P, Wosnik M.
    \newblock Reynolds Number Dependence of Cross-Flow Turbine Performance and
    Near-Wake Characteristics.
    \newblock In: Proceedings of the 2nd Marine Energy Technology Symposium
    METS2014. Seattle, WA; 2014. Available from:
    \url{http://hdl.handle.net/10919/49210}.

@@

    \bibitem{Bachant2015-JoT}
    Bachant P, Wosnik M.
    \newblock Characterising the near-wake of a cross-flow turbine.
    \newblock Journal of Turbulence. 2015 January;16(4):392--410.

    \bibitem{Bachant2016-RM2-data}
    Bachant P, Wosnik M, Gunawan B, Neary V. {UNH} {RM2} tow tank experiment:
    Reduced dataset and processing code; 2016.
    \newblock fig\textbf{share}. http://dx.doi.org/10.6084/m9.figshare.1373899.

@@

    \bibitem{Laneville1986}
    Laneville A, Vittecoq P.
    \newblock Dynamic Stall: The Case of the Vertical Axis Wind Turbine.
    \newblock Journal of Solar Energy Engineering. 1986 May;108:140--145.

    \bibitem{Mays1990}
    Mays ID, Morgan CA, Anderson MB, Powles SJR.
    \newblock Experience with the {VAWT} 850 demonstration project.
    \newblock In: Proceedings of European Community Wind Energy Conference; 1990. .

@@

    \bibitem{Antheaume2008}
    Antheaume S, Maıtre T, Achard JL.
    \newblock Hydraulic Darrieus turbines efficiency for free fluid flow conditions
    versus power farms conditions.
    \newblock Renewable Energy. 2008;33:2186--2198.

@@

    \bibitem{Amet2009}
    Amet E, Maitre T, Pellone C, Achard JL.
    \newblock {2D} Numerical Simulations of Blade-Vortex Interaction in a
    {D}arrieus Turbine.
    \newblock Journal of Fluids Engineering. 2009 November;131.

@@

    \bibitem{Joo2015}
    Joo S, Choi H, Lee J.
    \newblock Aerodynamic characteristics of two-bladed H-Darrieus at various
    solidities and rotating speeds.
    \newblock Energy. 2015;p. 1--13.

    \bibitem{Mertens2003}
    Mertens S, van Kuik G, van Bussel G.
    \newblock Performance of an {H}-{D}arrieus in the skewed flow on a roof.
    \newblock Journal of Solar Energy Engineering. 2003;125:443--440.
    \newblock Available from:
    \url{https://www.researchgate.net/profile/Gerard_Van_Bussel/publication/245367769_Performance_of_an_H-Darrieus_in_the_Skewed_Flow_on_a_Roof/links/0deec53bc12ee39ec4000000.pdf}.

    \bibitem{Bachant2014-RVAT-baseline}
    Bachant P, Wosnik M. {UNH-RVAT} baseline performance and near-wake
    measurements: Reduced dataset and processing code; 2014.
    \newblock fig\textbf{share}. http://dx.doi.org/10.6084/m9.figshare.1080781.
    \newblock Available from: \url{http://dx.doi.org/10.6084/m9.figshare.1080781}.

    \bibitem{Michelen2014}
    Michelen C, Neary VS, Murray JC, Barone M.
    \newblock {CACTUS} open source code for hydrokinetic turbine design and
    analysis: model performance evaluation and public dissemination as open
    source design tool.
    \newblock In: Proceedings of the 2nd Marine Energy Technology Symposium; 2014.
    .

    \bibitem{Bachant2016-Energies}
    Bachant P, Wosnik M.
    \newblock Effects of Reynolds Number on the Energy Conversion and Near-Wake
    Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine.
    \newblock Energies. 2016;9(73).

    \bibitem{Bachant2015-RM2-CAD}
    Bachant P, Wosnik M, Gunawan B, Neary V. 1:6 scale {RM2} cross-flow turbine
    {CAD} package; 2015.
    \newblock fig\textbf{share}. http://dx.doi.org/10.6084/m9.figshare.1373870.

@@

    \bibitem{Cavagnaro2014}
    Cavagnaro R, Polagye B.
    \newblock An Evaluation of Blockage Corrections for a Helical Cross-Flow
    Turbine.
    \newblock In: Proceedings of the 3rd Oxford Tidal Energy Workshop. Oxford, UK;
    2014. .

@@

    \bibitem{Kinzel2012}
    Kinzel M, Mulligan Q, Dabiri JO.
    \newblock Energy exchange in an array of vertical-axis wind turbines.
    \newblock Journal of Turbulence. 2012;13:1--13.

>>>>

The mechanical power, total rotor drag, and near-wake velocity of a 1:6 scale
model (1.075 m diameter) of the US Department of Energy's Reference Model
vertical-axis cross-flow turbine were measured experimentally in a towing tank,
to provide a comprehensive open dataset for validating numerical models.
Performance was measured for a range of tip speed ratios and at multiple
Reynolds numbers by varying the rotor's angular velocity and tow carriage speed,
respectively. A peak power coefficient $C_P = 0.37$ and rotor drag coefficient
$C_D = 0.84$ were observed at a tip speed ratio $\lambda_0 = 3.1$. A regime of
weak linear $Re$-dependence of the power coefficient was observed above a
turbine diameter Reynolds number $Re_D \approx 10^6$. The effects of support
strut drag on turbine performance were investigated by covering the rotor's NACA
0021 struts with cylinders. As expected, this modification drastically reduced
the rotor power coefficient. Strut drag losses were also measured for the NACA
0021 and cylindrical configurations with the rotor blades removed. For
$\lambda=\lambda_0$, wake velocity was measured at 1 m $(x/D=0.93)$ downstream.
Mean velocity, turbulence kinetic energy, and mean kinetic energy transport were
compared with results from a high solidity turbine acquired with the same test
apparatus. Like the high solidity case, mean vertical advection was calculated
to be the largest contributor to near-wake recovery. However, overall, lower
levels of streamwise wake recovery were calculated for the RM2 case---a
consequence of both the relatively low solidity and tapered blades reducing
blade tip vortex shedding---responsible for mean vertical advection---and lower
levels of turbulence caused by higher operating tip speed ratio and therefore
reduced dynamic stall. Datasets, code for processing and visualization, and a
CAD model of the turbine have been made publicly available.

@@

% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
%
\bibliographystyle{plos2015}
% \bibliography{library}

\begin{thebibliography}{10}

@@

    \bibitem{Neary2014a}
    Neary VS, Lawson M, Previsic M, Copping A, Hallett KC, A L, et~al.
    \newblock Methodology for design and economic analysis of marine energy
      conversion (MEC) technologies.
    \newblock In: Proceedings of the Marine Energy Technology Symposium (METS2014).
      Seattle, WA; 2014.

@@

    \bibitem{Murray2011}
    Murray J, Barone M.
    \newblock The Development of CACTUS, a Wind and Marine Turbine Performance
      Simulation Code.
    \newblock In: Proceedings of the 49th AIAA Aerospace Sciences Meeting including
      the New Horizons Forum and Aerospace Exposition; 2011.

@@

    \bibitem{Bachant2014}
    Bachant P, Wosnik M.
    \newblock Reynolds Number Dependence of Cross-Flow Turbine Performance and
      Near-Wake Characteristics.
    \newblock In: Proceedings of the 2nd Marine Energy Technology Symposium
      METS2014. Seattle, WA; 2014.Available from:
      \url{http://hdl.handle.net/10919/49210}.

@@

    \bibitem{Bachant2015-JoT}
    Bachant P, Wosnik M.
    \newblock Characterising the near-wake of a cross-flow turbine.
    \newblock Journal of Turbulence. 2015;16(4):392--410.
    \newblock doi:{10.1080/14685248.2014.1001852}.

    \bibitem{Bachant2016-RM2-data}
    Bachant P, Wosnik M, Gunawan B, Neary V. {UNH} {RM2} tow tank experiment:
      Reduced dataset and processing code; 2016.
    \newblock fig\textbf{share}.
      \url{http://dx.doi.org/10.6084/m9.figshare.1373899}.

@@

    \bibitem{Laneville1986}
    Laneville A, Vittecoq P.
    \newblock Dynamic Stall: The Case of the Vertical Axis Wind Turbine.
    \newblock Journal of Solar Energy Engineering. 1986;108:140--145.

    \bibitem{Mays1990}
    Mays ID, Morgan CA, Anderson MB, Powles SJR.
    \newblock Experience with the {VAWT} 850 demonstration project.
    \newblock In: Proceedings of European Community Wind Energy Conference; 1990.

@@

    \bibitem{Antheaume2008}
    Antheaume S, Ma{\^\i}tre T, Achard JL.
    \newblock Hydraulic {D}arrieus turbines efficiency for free fluid flow
      conditions versus power farms conditions.
    \newblock Renewable Energy. 2008;33:2186--2198.

@@

    \bibitem{Amet2009}
    Amet E, Ma{\^\i}tre T, Pellone C, Achard JL.
    \newblock {2D} Numerical Simulations of Blade-Vortex Interaction in a
      {D}arrieus Turbine.
    \newblock Journal of Fluids Engineering. 2009;131.
    \newblock doi:{10.1115/1.4000258}.

@@

    \bibitem{Joo2015}
    Joo S, Choi H, Lee J.
    \newblock Aerodynamic characteristics of two-bladed H-Darrieus at various
      solidities and rotating speeds.
    \newblock Energy. 2015; p. 1--13.

    \bibitem{Mertens2003}
    Mertens S, van Kuik G, van Bussel G.
    \newblock Performance of an {H}-{D}arrieus in the skewed flow on a roof.
    \newblock Journal of Solar Energy Engineering. 2003;125:443--440.
    \newblock doi:{10.1115/1.1629309}.

    \bibitem{Bachant2014-RVAT-baseline}
    Bachant P, Wosnik M. {UNH-RVAT} baseline performance and near-wake
      measurements: Reduced dataset and processing code; 2014.
    \newblock fig\textbf{share}.
      \url{http://dx.doi.org/10.6084/m9.figshare.1080781}.
    \newblock Available from: \url{http://dx.doi.org/10.6084/m9.figshare.1080781}.

    \bibitem{Michelen2014}
    Michelen C, Neary VS, Murray JC, Barone M.
    \newblock {CACTUS} open source code for hydrokinetic turbine design and
      analysis: model performance evaluation and public dissemination as open
      source design tool.
    \newblock In: Proceedings of the 2nd Marine Energy Technology Symposium; 2014.

    \bibitem{Bachant2016-Energies}
    Bachant P, Wosnik M.
    \newblock Effects of Reynolds Number on the Energy Conversion and Near-Wake
      Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine.
    \newblock Energies. 2016;9(73).
    \newblock doi:{10.3390/en9020073}.

    \bibitem{Bachant2015-RM2-CAD}
    Bachant P, Wosnik M, Gunawan B, Neary V. 1:6 scale {RM2} cross-flow turbine
      {CAD} package; 2015.
    \newblock fig\textbf{share}.
      \url{http://dx.doi.org/10.6084/m9.figshare.1373870}.

@@

    \bibitem{Cavagnaro2014}
    Cavagnaro R, Polagye B.
    \newblock An Evaluation of Blockage Corrections for a Helical Cross-Flow
      Turbine.
    \newblock In: Proceedings of the 3rd Oxford Tidal Energy Workshop. Oxford, UK;
      2014.

@@

    \bibitem{Kinzel2012}
    Kinzel M, Mulligan Q, Dabiri JO.
    \newblock Energy exchange in an array of vertical-axis wind turbines.
    \newblock Journal of Turbulence. 2012;13:1--13.
    \newblock doi:{10.1080/14685248.2012.712698}.
